---
title: "Regulating mechanisms for Schistosomiasis transmission"
author: "Veronica Malizia"
date: "07-03-2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
rm(list = ls())

.libPaths(c("C:/Program Files/R/R-4.1.2/library",.libPaths()))

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE,
                      fig.width=12, fig.height=10)
```

```{r setting, echo=FALSE, include=FALSE}

library(tidyverse)
library(readxl)
library(ggridges)
library(patchwork)
library(egg)
library(rstudioapi)
library(scales)

`%!in%` <- Negate(`%in%`)
geom_mean <- function(x){exp(mean(log(x)))}
ci <- function(x){quantile(x, probs=c(0.025, 0.975), na.rm = T)}
################

#Set folder
source.dir <- dirname(getActiveDocumentContext()$path)
  #"C:/Users/Z541213/Documents/Project/Model/Schisto_model"
setwd(source.dir)

#Load parameters
source("02_Parameters_Smansoni.R")
#Setting scenario
source("Setting_simulation_scenario.R")

```

# Simulation setting

```{r parameters, echo=FALSE, results='asis'}
library(knitr)
kable(caption = "Simulation setting and transmission parameters",
      read_excel(paste("Zetas_", exposure, "_func.xlsx", sep = "")) %>%
        filter(Endemicity == endem) %>%
        select(Endemicity,	Immunity, Snails,	DDF,	Zeta_grid_search,	Kw,	`Transmission on snails`) %>%
        mutate(`Transmission on snails` = format(`Transmission on snails`, scientific = T))
      )

```

# Simulation results

```{r loading population data, echo=FALSE}
#Load population output
#####Load collated results and produce multi-panel plots
pop.output.dir <- file.path(source.dir, "Output/Population")
res <- readRDS(file.path(pop.output.dir, 
               paste(setting, ".RDS", sep = "")))

# if(endem=="High" | endem=="Moderate"){
#   res <- res[- which(res$Immunity=="Absent" & res$Snails=="Absent" & res$DDF=="Absent"),]
# }
#Computing faded-out runs at pre-control ( soon before MDA)
faided <- res %>%
  filter(time==(parms$mda$start-1)*12) %>%
  group_by(Immunity, Snails, DDF) %>%
  summarise(faided_seed = length(which(eggs_prev_SAC==0))*100/seeds)
n_faided <- length(which(faided$faided_seed>0))

#Computing runs that get eliminated after MDA (check 50 ys after MDA):
eliminated <- res %>%
  filter(time==(parms$mda$end+50)*12) %>%
  group_by(Immunity, Snails, DDF) %>%
  summarise(eliminated_seed = length(which(eggs_prev_SAC==0))*100/seeds,
            ephp_seed = length(which(Heggs_prev<=0.01))*100/seeds)

#Average by seed
if(n_faided>0){
  res <- res[- which(res$time==(parms$mda$start-1)*12 & res$eggs_prev_SAC==0), ]
}
  
data_avg <- res %>%
  group_by(time, Immunity, Snails, DDF) %>%
  summarise(eggs_prev_SAC = mean(eggs_prev_SAC),
            eggs_prev_tot = mean(eggs_prev),
            PHI = mean(Heggs_prev_SAC),
            miracidiae = mean(miracidiae),
            cercariae = mean(cercariae),
            snail_inf = mean(inf_snail),
            snail_exp = mean(exp_snail),
            snail_prev = mean(inf_snail/(susc_snail+inf_snail+exp_snail)))

```

# Prevalence timelines

```{r failed runs, echo=FALSE, results='asis'}
library(knitr)

#if(endem=="Low"){
  kable(caption = "Faded-out runs at pre-control",
        faided %>%
          mutate(faided_seed = paste(faided_seed, "%", sep = " "))
        )


kable(caption = "Eliminated runs after 10 ys MDA to SAC",
      eliminated %>%
          mutate(eliminated_seed = paste(eliminated_seed, "%", sep = " "),
                 ephp_seed = paste(ephp_seed, "%", sep = " "))
      )
#}
```

## Prevalence of any infection in school-aged-children (SAC)

Solid lines show prevalence of infection in SAC. Dashed lines show the underlying prevalence of infection on snails (shedding).

```{r SAC prev, echo=FALSE}


Fig <- ggplot(data=data_avg, aes(x=time/12)) +
  geom_line(data = res, aes(y=eggs_prev_SAC*100,
                            group = interaction(DDF, seed),
                            colour = DDF), alpha = 0.01) +
  geom_line(aes(y=eggs_prev_SAC*100, colour = DDF), alpha = 3) +
  #geom_line(aes(y=PHI*100, colour = DDF), linetype = "longdash") +
  # geom_segment(data = prev_endPC,
  #              aes(x = 0, y = eggs_prev_SAC*100, xend = parms$mda$end, yend = eggs_prev_SAC*100, colour = DDF),
  #              linetype = "dashed") +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  scale_y_continuous(name = "Prevalence of infection in SAC (%) \n",
                     breaks = seq(0, 100, 20),
                     limits = c(0, 100),
                     expand = c(0, 0)) +
  scale_x_continuous(name = "\n Time [Years from last round of PC]",
                     breaks = seq(parms$mda$start-10, parms$mda$end+50, 10),
                     labels = seq(-20, 50, 10),
                     #limits = c(0, 1200),
                     expand = c(0, 0)) +
  coord_cartesian(xlim=c(parms$mda$start-10, parms$mda$end+50)) +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(legend.position="bottom",
        #axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5),
        plot.margin = margin(5, 10, 0, 10, "pt"),
        panel.spacing = unit(1.5, "lines"))

# tiff("Plots/Modeling_scenarios/PrevalenceSAC.tif", width=10, height=9, units = "in", res = 300)
Fig
# dev.off()
```

<!-- ## Zoom on MDA rounds -->

<!-- Solid lines show prevalence of infection in SAC. Dashed lines show the underlying prevalence of infection on snails (shedding). -->

<!-- ```{r SAC prevalence MDA, echo=FALSE} -->

<!-- #tiff("Plots/Modeling_scenarios/PrevalenceSAC_MDA.tif", width=10, height=9, units = "in", res = 300) -->

<!-- Fig +  -->

<!--   # geom_text(data=zetas, aes(x=170, y=80, label=my_tag),  -->

<!--   #           size=3) + -->

<!--   coord_cartesian(xlim=c(140, 170))  -->

<!-- #dev.off() -->

<!-- ``` -->

## Prevalence of heavy intensity infections in SAC

```{r heavy prev SAC, echo=FALSE}

Fig2 <- ggplot(data=data_avg, aes(x=time/12)) +
  geom_line(aes(y=PHI*100, colour = DDF)) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  # geom_text(data=text, aes(x=200, y=80, label=my_tag),
  #           size=3) +
  scale_y_continuous(name = "Prevalence of heavy infections (%) \n",
                     breaks = seq(0, 100, 5), #1 l - 2 m - 5 h
                     limits = c(0, 30), #2 l - 10 m - 30 h
                     expand = c(0, 0)) +
  scale_x_continuous(name = "\n Time [Years from last round of PC]",
                     breaks = seq(parms$mda$start-10, parms$mda$end+50, 10),
                     labels = seq(-20, 50, 10),
                     #limits = c(0, 1200),
                     expand = c(0, 0)) +
  coord_cartesian(xlim=c(parms$mda$start-10, parms$mda$end+50)) +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(legend.position="bottom",
        plot.margin = margin(5, 10, 0, 10, "pt"),
        panel.spacing = unit(1, "lines"))

#tiff("Plots/Modeling_scenarios/Prevalence_Heavy.tif", width=10, height=9, units = "in", res = 300)
Fig2
#dev.off()
```

<!-- ## Check: ratio of miracidiae over cercariae in the environment -->

<!-- ```{r mirac and cerc, echo=FALSE} -->

<!-- cercVSmirac <- ggplot(data_avg, aes(x=time/12)) + -->

<!--   geom_line(aes(y=miracidiae/cercariae, colour = DDF), alpha=0.5) + -->

<!--   facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both), scales = "free") + -->

<!--   scale_y_continuous(name = "Ratio miracidiae / cercariae", -->

<!--                      expand = c(0, 0)) + -->

<!--   scale_x_continuous(name = "Time [years]", -->

<!--                      expand = c(0, 0)) + -->

<!--   expand_limits(x = 0,y = 0) -->

<!-- cercVSmirac -->

<!-- ``` -->

# Individual-level results

```{r loading individual data, echo=FALSE, include=FALSE}

#Load individual output
#Collate results by seeds
ind.output.dir <- file.path(source.dir, paste("Output/Individual/", setting, sep = ""))

data_all <- list.files(path = ind.output.dir,  # Identify all output CSV files
                       pattern = "^Ind_out_seed", full.names = TRUE) %>%
  lapply(readRDS) %>%              # Store all files in list
  #lapply(read_csv, show_col_types = F) %>%
  bind_rows %>%
  filter(time == parms$mda$start-9 | time == parms$mda$end+1) #In the individual output, time is already in years


# Combine data sets into one
#Aggregate by age groups
#Filter one year of interest
#unique(data_all$time) #individual output contains time in years
#years <- c(81, 101, 151, 181) #c(51, 81, 101, 151, 161, 171, 181, 191)
# age_out <- data_all %>%
#   #filter(seed %!in% dead.seeds) %>%
#   mutate(age_group = case_when(age<=1 ~ "0_1",
#                                age>1 & age<=5 ~ "1_5",
#                                age>5 & age<=15 ~ "5_15",
#                                age>15 & age<=30 ~ "15_30",
#                                age>30 & age<=40 ~ "30_40",
#                                age>40 ~ "40_90")) %>%
#   group_by(seed, time, age_group, Immunity, Snails, DDF) %>% #sex not for now
#   summarise(epg = mean(ec*24), #geom_mean(ec*24+1), #means over individuals of that age group
#             wp = mean(tot_wp),
#             dwp = mean(cum_dwp),
#             rate = mean(rate))


age_out <- data_all %>%
  group_by(time, Immunity, Snails, DDF) %>%
  mutate(age_group = cut_number(age, n = 14)) %>%
  group_by(seed, time, age_group, Immunity, Snails, DDF) %>% #sex not for now
  summarise(avg_age_group = mean(age),
            epg = mean(ec*24), #geom_mean(ec*24+1), #means over individuals of that age group
            wp = mean(tot_wp),
            dwp = mean(cum_dwp),
            rate = mean(rate))

# age_out$age_group <- factor(age_out$age_group, levels = c("0_1",
#                                                           "1_5",
#                                                           "5_15",
#                                                           "15_30",
#                                                           "30_40",
#                                                           "40_90"))
age_out$time <- factor(as.factor(age_out$time),
                       levels = c(as.character(parms$mda$start-9), as.character(parms$mda$end+1)),
                       labels = c("Pre control",  "Post control"))

# saveRDS(age_out, file = file.path(ind.output.dir, "Avg_individual_output_pre&postmda.RDS"))

#Average over seeds
data_toplot <- age_out %>%
  #filter(!(Immunity == "Absent" & Snails== "Absent" & DDF== "Absent")) %>%
  group_by(age_group, time, Immunity, Snails, DDF) %>%
  summarise(avg_age_group = mean(avg_age_group),
            epg_mean = mean(epg),
            epg_lo = ci(epg)[1],
            epg_hi = ci(epg)[2],
            wp_mean = mean(wp),
            wp_lo = ci(wp)[1],
            wp_hi = ci(wp)[2],
            dwp_mean = mean(dwp),
            dwp_lo = ci(dwp)[1],
            dwp_hi = ci(dwp)[2],
            rate_mean = mean(rate),
            rate_lo = ci(rate)[1],
            rate_hi = ci(rate)[2])
```

```{r plot functions, echo=FALSE}
#Mean intensity
eggs <- ggplot(filter(data_toplot, DDF=="Mild"),
         aes(x=avg_age_group, y=epg_mean, group = interaction(DDF, Immunity)))+
  #geom_pointrange(aes(ymin=epg_lo, ymax=epg_hi, colour = DDF, shape = Immunity)) +
  geom_line(#data = filter(data_toplot, DDF=="Mild"),
            aes(colour = DDF, linetype = Immunity), size = 1) +
  #labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(time ~ Snails, labeller = labeller(.rows = label_both, .cols = label_both)) + #, scales = "free_y") +
  scale_y_continuous(name = "Egg counts (epg) \n",
                #breaks = seq(0, 10000, 200),
                #limits = c(0.5, 8000), #3000 l-m 8000 high
                expand = c(0, 0)) +
  scale_x_continuous(name = "\n Age [years]",
                     breaks = seq(0, 80, 10),
                     limits = c(0, 70),
                     expand = c(0, 0)) +
  expand_limits(x = 0,y = 0) +
  guides(shape = "none") +
  scale_color_manual(values = c("Mild" = hue_pal()(3)[2])) +
  scale_linetype_manual(values = c("Absent" = "solid", "Mild" = "dotted", "Strong" = "dashed")) +
  theme_bw() +
  theme(legend.position="bottom",
        plot.margin = margin(5, 10, 0, 10, "pt"),
        panel.spacing = unit(1, "lines"))

# tiff("Plots/Modeling_scenarios/Age profiles/Eggs.tif", width=10, height=9, units = "in", res = 300)
# eggs
# dev.off()

#Parasite establishment rate
rate <- ggplot(data_toplot, aes(x=avg_age_group, y=rate_mean, group = interaction(DDF, time)))+
  geom_pointrange(aes(ymin=rate_lo, ymax=rate_hi, colour = DDF)) +
  geom_line(aes(colour = DDF, linetype = time)) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  scale_y_continuous(name = "Parasite establishment rate \n",
                     #breaks = seq(0, 20, 2),
                     #limits = c(0.5, 80), #20 l-m 80 high
                     expand = c(0, 0)) +
  scale_x_continuous(name = "\n Age [years]",
                     breaks = seq(0, 80, 10),
                     limits = c(0, 70),
                     expand = c(0, 0)) +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(#axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    legend.position="bottom",
    plot.margin = margin(5, 10, 0, 10, "pt"),
    panel.spacing = unit(1, "lines"))

# tiff("Plots/Modeling_scenarios/Age profiles/Rate.tif", width=10, height=9, units = "in", res = 300)
# rate
# dev.off()

#Worms
worms <- ggplot(data_toplot, aes(x=avg_age_group, y=wp_mean, group = interaction(DDF, time)))+
  geom_pointrange(aes(ymin=wp_lo, ymax=wp_hi, colour = DDF)) +
  geom_line(aes(colour = DDF, linetype = time)) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) + #, scales = "free_y") +
  scale_y_continuous(name = "Worm load (pairs) \n",
                #breaks = seq(0, 10000, 200),
                #limits = c(0.5, 5000), #1000 l-m #5000 high
                expand = c(0, 0)) +
  scale_x_continuous(name = "\n Age [years]",
                     breaks = seq(0, 80, 10),
                     limits = c(0, 70),
                     expand = c(0, 0)) +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(#axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    legend.position="bottom",
    plot.margin = margin(5, 10, 0, 10, "pt"),
    panel.spacing = unit(1, "lines"))

# tiff("Plots/Modeling_scenarios/Age profiles/Worms.tif", width=10, height=9, units = "in", res = 300)
# worms
# dev.off()

#Dead worm pairs
dead_worms <- ggplot(data_toplot, aes(x=avg_age_group, y=dwp_mean, group = interaction(DDF, time)))+
  geom_pointrange(aes(ymin=dwp_lo, ymax=dwp_hi, colour = DDF)) +
  geom_line(aes(colour = DDF, linetype = time)) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  scale_y_continuous(name = "Cumulated dead worm (pairs) \n",
                #breaks = seq(0, 10000, 200),
                #limits = c(0.5, 1000),
                expand = c(0, 0)) +
  scale_x_continuous(name = "\n Age [years]",
                     breaks = seq(0, 80, 10),
                     limits = c(0, 70),
                     expand = c(0, 0)) +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(#axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    legend.position="bottom",
    plot.margin = margin(5, 10, 0, 10, "pt"),
    panel.spacing = unit(1, "lines"))

# tiff("Plots/Modeling_scenarios/Age profiles/Dead_worms.tif", width=10, height=9, units = "in", res = 300)
# dead_worms
# dev.off()
```

## Age-intensity profiles

```{r age-intensity, echo=FALSE}
eggs
```

## Check: worm distribution by age

```{r worms, echo=FALSE}
worms
```

## Check: parasite establishment rate

```{r establishment rate, echo=FALSE}
rate
```

## Check: cumulated dead worms by age

```{r dead worms, echo=FALSE}
dead_worms
```

<!-- ## Average worm pairs and epg in the whole population -->

<!-- ```{r avg worms, echo=FALSE, results='asis'} -->

<!-- library(knitr) -->

<!-- kable(caption = "Population mean and 95%-CI of worm burdens and observed epg", -->

<!--       data_all %>% -->

<!--         filter(time == 131) %>% -->

<!--         #filter(seed %!in% dead.seeds) %>% -->

<!--         group_by(Immunity, Snails, DDF) %>% #sex not for now -->

<!--         summarise(wp_mean = mean(tot_wp), -->

<!--                   wp_lo = ci(tot_wp)[1], -->

<!--                   wp_hi = ci(tot_wp)[2], -->

<!--                   epg_mean = mean(ec*24), #geom_mean(ec*24+1), #means over individuals of that sex-age group -->

<!--                   epg_lo = ci(ec*24)[1], -->

<!--                   epg_hi = ci(ec*24)[2]) -->

<!-- ) -->

<!-- ``` -->
