---
title: "Regulating mechanisms on Schistosomiasis transmission"
author: "Veronica Malizia"
date: '19-01-2023'
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())

.libPaths(c("C:/Program Files/R/R-4.1.2/library",.libPaths()))

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE,
                      fig.width=12, fig.height=10)
```



```{r setting, echo=FALSE, include=FALSE}

library(tidyverse)
library(readxl)
library(ggridges)
library(patchwork)
library(egg)
library(rstudioapi)

`%!in%` <- Negate(`%in%`)
geom_mean <- function(x){exp(mean(log(x)))}
ci <- function(x){quantile(x, probs=c(0.025, 0.975), na.rm = T)}
################
#SETTING THE SCENARIO
seeds <- 10

setting <- "High_Complete_Age-int" #"Moderate_setting_k=015_Age-int"
endem <- "Moderate"

#Set folder
source.dir <- dirname(getActiveDocumentContext()$path)
  #"C:/Users/Z541213/Documents/Project/Model/Schisto_model"
setwd(source.dir)
```

# Simulation setting

```{r parameters, echo=FALSE, results='asis'}
library(knitr)
kable(caption = "Simulaition setting and transmission parameters",
      read_excel("Zetas.xlsx") %>%
        filter(Endemicity == endem, Immunity != "Strong") %>%
        select(Endemicity,	Immunity, Snails,	DDF,	Zeta_grid_search,	Kw,	`Transmission on snails`) %>%
        mutate(`Transmission on snails` = format(`Transmission on snails`, scientific = T))
      )

```

# Simulation results

```{r loading population data, echo=FALSE}
#Load population output
#####Load collated results and produce multi-panel plots
pop.output.dir <- file.path(source.dir, "Output/Population")
res <- readRDS(file.path(pop.output.dir, 
               paste(setting, ".RDS", sep = "")))

#Average by seed
data_avg <- res %>%
  group_by(time, Immunity, Snails, DDF) %>%
  summarise(eggs_prev_SAC = mean(eggs_prev_SAC),
            PHI = mean(Heggs_prev),
            miracidiae = mean(miracidiae),
            cercariae = mean(cercariae),
            snail_inf = mean(inf_snail),
            snail_exp = mean(exp_snail),
            snail_prev = mean(inf_snail/(susc_snail+inf_snail+exp_snail)))

```

# Prevalence timelines

## Prevalence of any infection in school-aged-children (SAC)

Solid lines show prevalence of infection in SAC. Dashed lines show the underlying prevalence of infection on snails (shedding).

```{r SAC prev, echo=FALSE}
Fig <- ggplot(data=data_avg, aes(x=time/12)) +
  geom_line(aes(y=eggs_prev_SAC*100, colour = DDF)) +
  geom_line(aes(y=snail_prev*100, colour = DDF), linetype = "longdash") +
  #geom_line(data = res, aes(y = eggs_prev_SAC*100, colour = DDF), alpha = 0.3) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  # geom_text(data=text, aes(x=200, y=80, label=my_tag), 
  #           size=3) +
  scale_y_continuous(name = "Prevalence of infection in SAC (%) \n",
                     breaks = seq(0, 100, 20),
                     limits = c(0, 100),
                     expand = c(0, 0)) +
  scale_x_continuous(name = "\n Time [Years]",
                     #limits = c(0, 1200),
                     expand = c(0, 0)) +
  #coord_cartesian(xlim=c(500, (T*12))) +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(legend.position="bottom",
        plot.margin = margin(5, 10, 0, 10, "pt"),
        panel.spacing = unit(1, "lines")) 

# tiff("Plots/Modeling_scenarios/PrevalenceSAC.tif", width=10, height=9, units = "in", res = 300)
Fig 
# dev.off()
```

## Zoom on MDA rounds

Solid lines show prevalence of infection in SAC. Dashed lines show the underlying prevalence of infection on snails (shedding).

```{r SAC prevalence MDA, echo=FALSE}
#tiff("Plots/Modeling_scenarios/PrevalenceSAC_MDA.tif", width=10, height=9, units = "in", res = 300)
Fig + 
  # geom_text(data=zetas, aes(x=170, y=80, label=my_tag), 
  #           size=3) +
  coord_cartesian(xlim=c(140, 170)) 
#dev.off()

```

## Prevalence of heavy intensity infections in SAC

```{r heavy prev SAC, echo=FALSE}

Fig2 <- ggplot(data=data_avg, aes(x=time/12)) +
  geom_line(aes(y=PHI*100, colour = DDF)) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  # geom_text(data=text, aes(x=200, y=80, label=my_tag), 
  #           size=3) +
  scale_y_continuous(name = "Prevalence of heavy infections (%) \n",
                     breaks = seq(0, 10, 2),
                     limits = c(0, 10),
                     expand = c(0, 0)) +
  scale_x_continuous(name = "\n Time [Years]",
                     #limits = c(0, 1200),
                     expand = c(0, 0)) +
  #coord_cartesian(xlim=c(500, (T*12))) +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(legend.position="bottom",
        plot.margin = margin(5, 10, 0, 10, "pt"),
        panel.spacing = unit(1, "lines")) 

#tiff("Plots/Modeling_scenarios/Prevalence_Heavy.tif", width=10, height=9, units = "in", res = 300)
Fig2 
#dev.off()
```

## Check: ratio of miracidiae over cercariae in the environment
```{r mirac and cerc, echo=FALSE}
cercVSmirac <- ggplot(data_avg, aes(x=time/12)) +
  geom_line(aes(y=miracidiae/cercariae, colour = DDF), alpha=0.5) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both), scales = "free") +
  scale_y_continuous(name = "Ratio miracidiae / cercariae",
                     expand = c(0, 0)) +
  scale_x_continuous(name = "Time [years]",
                     expand = c(0, 0)) +
  expand_limits(x = 0,y = 0)

cercVSmirac
```

# Individual-level results

```{r loading individual data, echo=FALSE, include=FALSE}

#Load individual output
#Collate results by seeds
ind.output.dir <- file.path(source.dir, paste("Output/Individual/", setting, sep = "")) 

data_all <- list.files(path = ind.output.dir,  # Identify all output CSV files
                       pattern = "*.RDS", full.names = TRUE) %>% 
  lapply(readRDS) %>%              # Store all files in list
  #lapply(read_csv, show_col_types = F) %>%
  bind_rows %>%
  filter(time == 131)

# Combine data sets into one
#Aggregate by age groups
#Filter one year of interest
#unique(data_all$time) #individual output contains time in years
#years <- c(81, 101, 151, 181) #c(51, 81, 101, 151, 161, 171, 181, 191)
age_out <- data_all %>%
  #filter(seed %!in% dead.seeds) %>%
  mutate(age_group = case_when(age<=1 ~ "0_1",
                               age>1 & age<=5 ~ "1_5",
                               age>5 & age<=15 ~ "5_15",
                               age>15 & age<=30 ~ "15_30",
                               age>30 & age<=40 ~ "30_40",
                               age>40 ~ "40_90")) %>% 
  group_by(time, age_group, Immunity, Snails, DDF) %>% #sex not for now
  summarise(epg_mean = mean(ec*24), #geom_mean(ec*24+1), #means over individuals of that sex-age group
            wp_mean = mean(tot_wp),
            dwp_mean = mean(cum_dwp), 
            rate_mean = mean(rate),
            epg_lo = ci(ec*24)[1],
            epg_hi = ci(ec*24)[2],
            wp_lo = ci(tot_wp)[1],
            wp_hi = ci(tot_wp)[2],
            dwp_lo = ci(cum_dwp)[1],
            dwp_hi = ci(cum_dwp)[2],
            rate_lo = ci(rate)[1],
            rate_hi = ci(rate)[2]) 

age_out$age_group <- factor(age_out$age_group, levels = c("0_1",
                                                          "1_5",
                                                          "5_15",
                                                          "15_30",
                                                          "30_40",
                                                          "40_90"))

#save(age_out, file = file.path(output.dir, "Collated_time131.RData"))

#Average over seeds
data_toplot <- age_out 

# %>%
#   #filter(!(Immunity == "Absent" & Snails== "Absent" & DDF== "Absent")) %>%
#   group_by(age_group, Immunity, Snails, DDF) %>%
#   summarise(epg_mean = mean(epg),
#             epg_lo = ci(epg)[1],
#             epg_hi = ci(epg)[2],
#             wp_mean = mean(wp),
#             wp_lo = ci(wp)[1],
#             wp_hi = ci(wp)[2],
#             dwp_mean = mean(dwp),
#             dwp_lo = ci(dwp)[1],
#             dwp_hi = ci(dwp)[2],
#             rate_mean = mean(rate),
#             rate_lo = ci(rate)[1],
#             rate_hi = ci(rate)[2])
```

```{r plot functions, echo=FALSE}
#Mean intensity
eggs <- ggplot(data_toplot, aes(x=age_group, y=epg_mean+1, group = DDF))+
  geom_pointrange(aes(ymin=epg_lo+1, ymax=epg_hi+1, colour = DDF)) +
  geom_line(aes(colour = DDF)) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  scale_y_log10(name = "Observed egg counts (epg) + 1 \n",
                     #breaks = seq(0, 10000, 200),
                limits = c(0.5, 3000),
                     #expand = c(0, 0)
                ) +
  scale_x_discrete(name = "\n Age group [years]") +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(#axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position="bottom",
        plot.margin = margin(5, 10, 0, 10, "pt"),
        panel.spacing = unit(1, "lines")) 

# tiff("Plots/Modeling_scenarios/Age profiles/Eggs.tif", width=10, height=9, units = "in", res = 300)
# eggs
# dev.off()

#Parasite establishment rate
rate <- ggplot(data_toplot, aes(x=age_group, y=rate_mean+0.5, group = DDF))+
  geom_pointrange(aes(ymin=rate_lo+0.5, ymax=rate_hi+0.5, colour = DDF)) +
  geom_line(aes(colour = DDF)) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  scale_y_log10(name = "Parasite establishment rate + 0.5 \n",
                     #breaks = seq(0, 20, 2),
                     limits = c(0.5, 20),
                     #expand = c(0, 0)
  ) +
  scale_x_discrete(name = "\n Age group [years]") +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(#axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    legend.position="bottom",
    plot.margin = margin(5, 10, 0, 10, "pt"),
    panel.spacing = unit(1, "lines")) 

# tiff("Plots/Modeling_scenarios/Age profiles/Rate.tif", width=10, height=9, units = "in", res = 300)
# rate
# dev.off()

#Worms
worms <- ggplot(data_toplot, aes(x=age_group, y=wp_mean+0.5, group = DDF))+
  geom_pointrange(aes(ymin=wp_lo+0.5, ymax=wp_hi+0.5, colour = DDF)) +
  geom_line(aes(colour = DDF)) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  scale_y_log10(name = "Worm load (pairs) + 0.5 \n",
                #breaks = seq(0, 10000, 200),
                limits = c(0.5, 1000),
                #expand = c(0, 0)
  ) +
  scale_x_discrete(name = "\n Age group [years]") +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(#axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    legend.position="bottom",
    plot.margin = margin(5, 10, 0, 10, "pt"),
    panel.spacing = unit(1, "lines")) 

# tiff("Plots/Modeling_scenarios/Age profiles/Worms.tif", width=10, height=9, units = "in", res = 300)
# worms
# dev.off()

#Dead worm pairs
dead_worms <- ggplot(data_toplot, aes(x=age_group, y=dwp_mean+0.5, group = DDF))+
  geom_pointrange(aes(ymin=dwp_lo+0.5, ymax=dwp_hi+0.5, colour = DDF)) +
  geom_line(aes(colour = DDF)) +
  labs(title = paste(endem, "endemicity setting", sep = " ")) +
  facet_grid(Snails ~ Immunity, labeller = labeller(.rows = label_both, .cols = label_both)) +
  scale_y_log10(name = "Cumulated dead worm (pairs) + 0.5 \n",
                #breaks = seq(0, 10000, 200),
                limits = c(0.5, 10000),
                #expand = c(0, 0)
  ) +
  scale_x_discrete(name = "\n Age group [years]") +
  expand_limits(x = 0,y = 0) +
  theme_bw() +
  theme(#axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    legend.position="bottom",
    plot.margin = margin(5, 10, 0, 10, "pt"),
    panel.spacing = unit(1, "lines")) 

# tiff("Plots/Modeling_scenarios/Age profiles/Dead_worms.tif", width=10, height=9, units = "in", res = 300)
# dead_worms
# dev.off()
```

## Age-intensity profiles

```{r age-intensity, echo=FALSE}
eggs
```

## Check: worm distribution by age

```{r worms, echo=FALSE}
worms
```

## Check: parasite establishment rate

```{r establishment rate, echo=FALSE}
rate
```

## Check: cumulated dead worms by age

```{r dead worms, echo=FALSE}
dead_worms
```

## Average worm pairs and epg in the whole population

```{r avg worms, echo=FALSE, results='asis'}
library(knitr)
kable(caption = "Population mean and 95%-CI of worm burdens and observed epg",
      data_all %>%
        filter(time == 131) %>%
        #filter(seed %!in% dead.seeds) %>%
        group_by(Immunity, Snails, DDF) %>% #sex not for now
        summarise(wp_mean = mean(tot_wp),
                  wp_lo = ci(tot_wp)[1],
                  wp_hi = ci(tot_wp)[2],
                  epg_mean = mean(ec*24), #geom_mean(ec*24+1), #means over individuals of that sex-age group
                  epg_lo = ci(ec*24)[1],
                  epg_hi = ci(ec*24)[2])
)
```
